---
title: "STAT 4310 - Project"
author: "Group E: Chineze Embodi, Vaughn Jorgensen, Braxton Wilson"
date: "2023-04-26"
output:
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE)
```

```{r, warning=FALSE, message=FALSE, include=FALSE}
library(wooldridge)
library(kableExtra)
library(ggplot2)
library(quantmod)
```

## Introduction

**The Alcohol data set comes from the Woolridge package. It contains 33 variables with 9822 observations. Some of these variables include alcohol abuse, employment status, age, years of schooling, marital status, family size, and more.**

## Alcohol Data 

**The alcohol data contains several (20) categorical variables (status, married, white, exhealth, vghealth, goodhealth, fairhealth, northeast, midwest, south, centcity, outercity, qrt1, qrt2, qrt3, mothalc, fathalc, livealc, inwf, employ), but only status will be converted to a factor since all other categorical variables only have two levels. There are no missing values in any of the columns.**

```{r echo=FALSE}
data("alcohol")

metadata <- data.frame(Variable = c("abuse", "status", "unemrate", "age", "educ", "married", "famsize", "white", "exhealth", "vghealth", "goodhealth", "fairhealth", "northeast", "midwest", "south", "centcity", "outercity", "qrt1", "qrt2", "qrt3", "beertax", "cigtax", "ethanol", "mothalc", "fathalc", "livealc", "inwf", "employ", "agesq", "beertaxsq", "cigtaxsq", "ethanolsq", "educsq"), 
                       Description =  c(' = 1 if abuse alcohol',' out of workforce = 1; unemployed = 2, employed = 3',' state unemployment rate',' age in years',' years of schooling',' = 1 if married',' family size',' = 1 if white',' = 1 if in excellent health',' = 1 if in very good health',' = 1 if in good health',' = 1 if in fair health',' = 1 if live in northeast',' = 1 if live in midwest',' = 1 if live in south',' = 1 if live in central city of MSA',' = 1 if in outer city of MSA',' = 1 if interviewed in first quarter',' = 1 if interviewed in second quarter',' = 1 if interviewed in third quarter',' state excise tax, $ per gallon',' state cigarette tax, cents per pack',' state per-capita ethanol consumption',' = 1 if mother an alcoholic',' = 1 if father an alcoholic',' = 1 if lived with alcoholic',' = 1 if status > 1','  = 1 if employed', ' age^2', ' beertax^2', ' cigtax^2', ' ethanol^2', ' educ^2'))

kable_styling(kbl(metadata, booktabs = T, format = "latex"), latex_options = "striped")
```

\newpage

```{r echo=FALSE}
colSums(is.na(alcohol)) # no NA in any columns

str(alcohol)

# getting rid of squared attributes
gross <- c("agesq", "beertaxsq", "cigtaxsq", "ethanolsq", "educsq")
alcohol <- alcohol[ , !names(alcohol) %in% gross]

# converting binary/categorical variables into factors
alcohol$status <- as.factor(alcohol$status)
# alcohol$married <- as.factor(alcohol$married)
# alcohol$white <- as.factor(alcohol$white)
# alcohol$exhealth <- as.factor(alcohol$exhealth)
# alcohol$vghealth <- as.factor(alcohol$vghealth)
# alcohol$goodhealth <- as.factor(alcohol$goodhealth)
# alcohol$fairhealth <- as.factor(alcohol$fairhealth)
# alcohol$northeast <- as.factor(alcohol$northeast)
# alcohol$midwest <- as.factor(alcohol$midwest)
# alcohol$south <- as.factor(alcohol$south)
# alcohol$centcity <- as.factor(alcohol$centcity)
# alcohol$outercity <- as.factor(alcohol$outercity)
# alcohol$qrt1 <- as.factor(alcohol$qrt1)
# alcohol$qrt2 <- as.factor(alcohol$qrt2)
# alcohol$qrt3 <- as.factor(alcohol$qrt3)
# alcohol$mothalc <- as.factor(alcohol$mothalc)
# alcohol$fathalc <- as.factor(alcohol$fathalc)
# alcohol$livealc <- as.factor(alcohol$livealc)
# alcohol$inwf <- as.factor(alcohol$inwf)
# alcohol$employ <- as.factor(alcohol$employ)

head(alcohol)
```


```{r}
table(alcohol$abuse) # count for yes/1 vs no/0 alcohol abuse
```

**In our data set, we can see that there are 8848 observations of individuals who do not abuse alcohol (0) and 974 observations of alcohol abusers (1). This severe class imbalance may prove to be an issue.**

\newpage 

## Regression Analysis

**In our regression analysis, we will be using the abuse variable as our response and all others as predictors (excluding squared variables). The abuse variable will tell is if alcohol is abused (1) or if alcohol is not abused (0). Abuse was chosen as the response because it stands out as the best option based on the other variables in this data set. Additionally, it would be interesting to see which variables are determining factors in alcohol abuse.**  

**We will be utilizing the generalized linear model with a binomial distribution. This way, we can perform logistic regression on our categorical response variable.**

```{r}
model <- glm(abuse ~ ., family = "binomial", data = alcohol)
summary(model)

rsefull <- sqrt(deviance(model)/df.residual(model))
rsefull

# McFadden's R^2 -- Excellent fit considered to be 0.2-0.4
rsquafull <- with(summary(model), 1- deviance/null.deviance)
rsquafull
```

**In our full model, the variables that are statistically significant to our model at the 5% significance level are educ, famsize, white, centcity, ethanol, mothalc, and fathalc. Note the AIC score of 6248.1 which we will compare to our other models. The standard error using deviance and df comes out to 0.795. McFadden's $R^2$ comes out to 0.025 (good fit considered to be 0.2-0.4).**

```{r}
modred <- step(model, trace = 0)
summary(modred)

# RSE
rse <- sqrt(deviance(modred)/df.residual(modred))
rse

# McFadden's R^2 -- Excellent fit considered to be 0.2-0.4
rsqua <- with(summary(modred), 1- deviance/null.deviance)
rsqua
```

**After reducing our model, we went from 28 variables to 9 variables. This leaves us with the variables educ, famsize, white, exhealth, centcity, cigtax, ethanol, mothalc, and fathalc. The AIC dropped from 6248.1 to 6220.7 which may mostly be due to a decrease in variables. The RSE remained the same (0.795) but the McFadden's $R^2$ actually decreased to 0.023.**

```{r}
# residuals
res <- residuals(modred, type = "deviance")
qqnorm(res) # Should have normal distribution if model fits
qqline(res) # they do not...
plot(res) # should be around 0--if not they may be outliers
```

**The residuals of our model should have a normal distribution if our model fits; however, we can see that based on our qqplot that our model is not adequate. Additionally, we can see in our residual plot that many of our values are not close to 0 which promotes our models inadequacy and may suggest outliers. Let's investigate using cooks distance.**

```{r}
# cooks distance
cooks <- cooks.distance(modred)
plot(cooks) # lots of outliers
summary(cooks)
table(alcohol[cooks < 1.846e-05, "abuse"])
table(alcohol[cooks < 0.00085, "abuse"])

model2 <- glm(abuse ~ ., family = "binomial", data = subset(alcohol, cooks < 0.00085)) 
# 1.846e-05 from Q3--could not converge so chose number low enough to not get warning
modred2 <- step(model2, trace = 0)
summary(modred2)

# RSE
rse.cook <- sqrt(deviance(modred2)/df.residual(modred2))
rse.cook

# R^2
rsqua.cook <- with(summary(modred2), 1- deviance/null.deviance)
rsqua.cook # 0.023 => 0.089 -- slight improvement

rescook <- residuals(modred2, type = "deviance")
qqnorm(rescook) # Should have normal distribution if model fits
qqline(rescook) # they do not...
plot(rescook) # should be around 0
```

**Using cooks distance, our models AIC dropped even more from 6220.7 to 4121.8. The RSE also decreased from 0.795 to 0.659, and the McFadden's $R^2$ increased from 0.023 to 0.089. When investigating the residuals, they still are not normal or around 0; however, it is an improvement. We could definitely improve our model further if there were more abuse = 1 observations in our data set in order to get a model to converge with a smaller subset.**

```{r}
## fitted values in probabilities
fitted.values <- modred2$fitted.values

## prediction using 0,1
fitted <- ifelse(fitted.values >.5, 1,0)

table(alcohol[cooks < 0.00085, "abuse"], fitted)
```

------------------------------------------------------------------------------------------

\newpage

# Stock Analysis


```{r echo = FALSE}
## 2 year period will be from 2021 to 2022
start <- as.Date("2020-12-31")
end <- as.Date("2022-12-31")

### Will comopare 3 energy companies
## stock 1 - Sclumberger Ltd. (SLB)
SLB <- getSymbols("SLB", from = start, to = end, auto.assign = F)
SLB.close <- SLB$SLB.Close
SLB.return <- dailyReturn(SLB.close)
# annualized return
SLB.mu.ann <- mean(SLB.return) * 252
# annualized risk
SLB.sd.ann <- sd(SLB.return) * sqrt(252)

## stock 2 - Halliburton Company (HAL)
HAL <- getSymbols("HAL", from = start, to = end, auto.assign = F)
HAL.close <- HAL$HAL.Close
HAL.return <- dailyReturn(HAL.close)
# annualized return
HAL.mu.ann <- mean(HAL.return) * 252
# annualized risk
HAL.sd.ann <- sd(HAL.return) * sqrt(252)

## stock 3 - CenterPoint Energy Inc (CNP)
CNP <- getSymbols("CNP", from = start, to = end, auto.assign = F)
CNP.close <- CNP$CNP.Close
CNP.return <- dailyReturn(CNP.close)
# annualized return
CNP.mu.ann <- mean(CNP.return) * 252
# annualized risk
CNP.sd.ann <- sd(CNP.return) * sqrt(252)
```

```{r echo = FALSE}
bench <- getSymbols.yahoo("^GSPC", from = start, to = end, periodicity = "daily", auto.assign = F)[ , 4]
bench.returns <- dailyReturn(bench) 

bench.CP <- cumprod(1 + bench.returns)
# Closing Price Plots for SLB, HAL, CNP
SLB.CP <- cumprod(1 + SLB.return)
HAL.CP <- cumprod(1 + HAL.return)
CNP.CP <- cumprod(1 + CNP.return)

# enplot <- plot(SLB.CP, type = "l", ylim = c(0, 3), col = "blue", main = "Closing Prices: SLB-Blue, HAL-Red, CNP-Green")
# enplot <- lines(HAL.CP, type = "l", col = "red")
# enplot <- lines(CNP.CP, type = "l", col = "green")
# enplot
# 
# enplotb <- plot(bench.CP, type = "l", ylim = c(0, 3), col = "black", main = "CP: Market-Black, SLB-Blue, HAL-Red, CNP-Green")
# enplotb <- lines(SLB.CP, type = "l", col = "blue")
# enplotb <- lines(HAL.CP, type = "l", col = "red")
# enplotb <- lines(CNP.CP, type = "l", col = "green")
# enplotb
#legend("topleft", legend = c("SLB", "HAL", "CNP"), fill = c("blue", "red", "green"), title = "stocks")
```



```{r echo = FALSE}
## Reading Treasury Risk-free rate
# daily risk-free data
ff <- read.csv(file.choose(), head = T, skip = 4) # choose ffdaily data
ff.date <- as.Date(ff$X, format = "%Y%m%d")
ff$date <- ff.date
ff.new <- ff[ff$date >= start & ff$date <= end, ]
#head(ff.new)

# SLB
SLB.Ret.df <- data.frame(SLB.return)
SLB.Ret.df$date <- index(SLB.return)
SLB.data <- merge(SLB.Ret.df, ff.new, by.x = "date", all.x = T)

# HAL
HAL.Ret.df <- data.frame(HAL.return)
HAL.Ret.df$date <- index(HAL.return)
HAL.data <- merge(HAL.Ret.df, ff.new, by.x = "date", all.x = T)

# CNP
CNP.Ret.df <- data.frame(CNP.return)
CNP.Ret.df$date <- index(CNP.return)
CNP.data <- merge(CNP.Ret.df, ff.new, by.x = "date", all.x = T)

## Benchmark return
# annualized return
bench.mu.ann <- mean(bench.returns) * 252
# annualized risk
bench.sd.ann <- sd(bench.returns) * sqrt(252)

## beta & r^2
ff.newnew <- head(ff.new, -2) # last 2 rows are NA
# benchmark excess
bench.excess <- bench.returns - ff.newnew$RF

# SLB
SLB.excess <- SLB.return - ff.newnew$RF
SLB.beta <- coefficients(lm(SLB.excess ~ bench.excess))[2]
SLB.r2 <- summary(lm(SLB.excess ~ bench.excess))$r.squared

# HAL
HAL.excess <- HAL.return - ff.newnew$RF
HAL.beta <- coefficients(lm(HAL.excess ~ bench.excess))[2]
HAL.r2 <- summary(lm(HAL.excess ~ bench.excess))$r.squared

# CNP
CNP.excess <- CNP.return - ff.newnew$RF
CNP.beta <- coefficients(lm(CNP.excess ~ bench.excess))[2]
CNP.r2 <- summary(lm(CNP.excess ~ bench.excess))$r.squared

# PE ratio from yahoo finance
PESLB <- 22.02
PEHAL <- 19.72
PECNP <- 19.19

SLByahbeta <- 1.78
HALyahbeta <- 2.13
CNPyahbeta <- 0.88
```


```{r echo=FALSE}
### Braxton stocks
## ann return and risk
## stock 1 - Lowes (LOW)
LOW <- getSymbols("LOW", from = start, to = end, auto.assign = F)
LOW.close <- LOW$LOW.Close
LOW.return <- dailyReturn(LOW.close)
# annualized return
LOW.mu.ann <- mean(LOW.return) * 252
# annualized risk
LOW.sd.ann <- sd(LOW.return) * sqrt(252)

## stock 2 - Target (TGT)
TGT <- getSymbols("TGT", from = start, to = end, auto.assign = F)
TGT.close <- TGT$TGT.Close
TGT.return <- dailyReturn(TGT.close)
# annualized return
TGT.mu.ann <- mean(TGT.return) * 252
# annualized risk
TGT.sd.ann <- sd(TGT.return) * sqrt(252)

## stock 3 - Wal-Mart (WMT)
WMT <- getSymbols("WMT", from = start, to = end, auto.assign = F)
WMT.close <- WMT$WMT.Close
WMT.return <- dailyReturn(WMT.close)
# annualized return
WMT.mu.ann <- mean(WMT.return) * 252
# annualized risk
WMT.sd.ann <- sd(WMT.return) * sqrt(252)

## Closing Price Plot
# Closing Price Plots for LOW, TGT, WMT
LOW.CP <- cumprod(1 + LOW.return)
TGT.CP <- cumprod(1 + TGT.return)
WMT.CP <- cumprod(1 + WMT.return)

# stoplot <- plot(LOW.CP, type = "l", ylim = c(0, 3), col = "blue", main = "Closing Prices: LOW-Blue, TGT-Red, WMT-Green")
# stoplot <- lines(TGT.CP, type = "l", col = "red")
# stoplot <- lines(WMT.CP, type = "l", col = "green")
# stoplot
#  # compared to market
# stoplotb <- plot(bench.CP, type = "l", ylim = c(0, 3), col = "black", main = "CP: Market-Black, LOW-Blue, TGT-Red, WMT-Green")
# stoplotb <- lines(LOW.CP, type = "l", col = "blue")
# stoplotb <- lines(TGT.CP, type = "l", col = "red")
# stoplotb <- lines(WMT.CP, type = "l", col = "green")
# stoplotb

# beta and p/e
# LOW
LOW.Ret.df <- data.frame(LOW.return)
LOW.Ret.df$date <- index(LOW.return)
LOW.data <- merge(LOW.Ret.df, ff.new, by.x = "date", all.x = T)

# TGT
TGT.Ret.df <- data.frame(TGT.return)
TGT.Ret.df$date <- index(TGT.return)
TGT.data <- merge(TGT.Ret.df, ff.new, by.x = "date", all.x = T)

# WMT
WMT.Ret.df <- data.frame(WMT.return)
WMT.Ret.df$date <- index(WMT.return)
WMT.data <- merge(WMT.Ret.df, ff.new, by.x = "date", all.x = T)
## beta & r^2

# LOW
LOW.excess <- LOW.return - ff.newnew$RF
LOW.beta <- coefficients(lm(LOW.excess ~ bench.excess))[2]

# TGT
TGT.excess <- TGT.return - ff.newnew$RF
TGT.beta <- coefficients(lm(TGT.excess ~ bench.excess))[2]

# WMT
WMT.excess <- WMT.return - ff.newnew$RF
WMT.beta <- coefficients(lm(WMT.excess ~ bench.excess))[2]

PELOW <- 20.75
PETGT <- 27.12
PEWMT <- 35.53

LOWyahbeta <- 1.07
TGTyahbeta <- 1.02
WMTyahbeta <- 0.49
```


```{r echo=FALSE}
### Chineze stocks
## ann return and risk
## stock 1 - MGM Resorts International (MGM)
MGM <- getSymbols("MGM", from = start, to = end, auto.assign = F)
MGM.close <- MGM$MGM.Close
MGM.return <- dailyReturn(MGM.close)
# annualized return
MGM.mu.ann <- mean(MGM.return) * 252
# annualized risk
MGM.sd.ann <- sd(MGM.return) * sqrt(252)

## stock 2 - First Republic Bank (FRC)
FRC <- getSymbols("FRC", from = start, to = end, auto.assign = F)
FRC.close <- FRC$FRC.Close
FRC.return <- dailyReturn(FRC.close)
# annualized return
FRC.mu.ann <- mean(FRC.return) * 252
# annualized risk
FRC.sd.ann <- sd(FRC.return) * sqrt(252)

## stock 3 - Southwest Airlines Co. (LUV)
LUV <- getSymbols("LUV", from = start, to = end, auto.assign = F)
LUV.close <- LUV$LUV.Close
LUV.return <- dailyReturn(LUV.close)
# annualized return
LUV.mu.ann <- mean(LUV.return) * 252
# annualized risk
LUV.sd.ann <- sd(LUV.return) * sqrt(252)

## Closing Price Plot
# Closing Price Plots for MGM, FRC, LUV
MGM.CP <- cumprod(1 + MGM.return)
FRC.CP <- cumprod(1 + FRC.return)
LUV.CP <- cumprod(1 + LUV.return)

# enplot <- plot(MGM.CP, type = "l", ylim = c(0, 3), col = "gold", main = "Closing Prices: MGM-Gold, FRC-Green, LUV-Red")
# enplot <- lines(FRC.CP, type = "l", col = "green")
# enplot <- lines(LUV.CP, type = "l", col = "red")
# enplot
#  # compared to market
# enplotb <- plot(bench.CP, type = "l", ylim = c(0, 3), col = "black", main = "CP: Market-Black, MGM-Gold, FRC-Green, LUV-Red")
# enplotb <- lines(MGM.CP, type = "l", col = "gold")
# enplotb <- lines(FRC.CP, type = "l", col = "green")
# enplotb <- lines(LUV.CP, type = "l", col = "red")
# enplotb

# beta and p/e
# MGM
MGM.Ret.df <- data.frame(MGM.return)
MGM.Ret.df$date <- index(MGM.return)
MGM.data <- merge(MGM.Ret.df, ff.new, by.x = "date", all.x = T)

# FRC
FRC.Ret.df <- data.frame(FRC.return)
FRC.Ret.df$date <- index(FRC.return)
FRC.data <- merge(FRC.Ret.df, ff.new, by.x = "date", all.x = T)

# LUV
LUV.Ret.df <- data.frame(LUV.return)
LUV.Ret.df$date <- index(LUV.return)
LUV.data <- merge(LUV.Ret.df, ff.new, by.x = "date", all.x = T)
## beta & r^2

# MGM
MGM.excess <- MGM.return - ff.newnew$RF
MGM.beta <- coefficients(lm(MGM.excess ~ bench.excess))[2]

# FRC
FRC.excess <- FRC.return - ff.newnew$RF
FRC.beta <- coefficients(lm(FRC.excess ~ bench.excess))[2]

# LUV
LUV.excess <- LUV.return - ff.newnew$RF
LUV.beta <- coefficients(lm(LUV.excess ~ bench.excess))[2]

PEMGM <- 12.86
PEFRC <- 1.68
PELUV <- 36.95

MGMyahbeta <- 2.07
FRCyahbeta <- 1.01
LUVyahbeta <- 1.14
```



```{r echo=FALSE}
# SLB, HAL, CNP
engplt <- ggplot() + geom_line(data = SLB.CP, aes(x = index(SLB.CP), y = daily.returns, color = "SLB")) + geom_line(data = HAL.CP, aes(x = index(HAL.CP), y = daily.returns, color = "HAL")) + geom_line(data = CNP.CP, aes(x = index(CNP.CP), y = daily.returns, color = "CNP")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("SLB" = "blue", "HAL" = "red", "CNP" = "green"))
engplt

engmrkplt <- ggplot() + geom_line(data = SLB.CP, aes(x = index(SLB.CP), y = daily.returns, color = "SLB")) + geom_line(data = HAL.CP, aes(x = index(HAL.CP), y = daily.returns, color = "HAL")) + geom_line(data = CNP.CP, aes(x = index(CNP.CP), y = daily.returns, color = "CNP")) + geom_line(data = bench.CP, aes(x = index(bench.CP), y = daily.returns, color = "Market")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("SLB" = "blue", "HAL" = "red", "CNP" = "green", "Market" = "black"))
engmrkplt
```

\newpage

```{r echo=FALSE}
# LOW, TGT, WMT
# blue red green
stoplt <- ggplot() + geom_line(data = LOW.CP, aes(x = index(LOW.CP), y = daily.returns, color = "LOW")) + geom_line(data = TGT.CP, aes(x = index(TGT.CP), y = daily.returns, color = "TGT")) + geom_line(data = WMT.CP, aes(x = index(WMT.CP), y = daily.returns, color = "WMT")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("LOW" = "blue", "TGT" = "red", "WMT" = "green"))
stoplt

stomrkplt <- ggplot() + geom_line(data = LOW.CP, aes(x = index(LOW.CP), y = daily.returns, color = "LOW")) + geom_line(data = TGT.CP, aes(x = index(TGT.CP), y = daily.returns, color = "TGT")) + geom_line(data = WMT.CP, aes(x = index(WMT.CP), y = daily.returns, color = "WMT")) + geom_line(data = bench.CP, aes(x = index(bench.CP), y = daily.returns, color = "Market")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("LOW" = "blue", "TGT" = "red", "WMT" = "green", "Market" = "black"))
stomrkplt
```

\newpage

```{r echo=FALSE}
# MGM, FRC, LUV
# gold green red
chplt <- ggplot() + geom_line(data = MGM.CP, aes(x = index(MGM.CP), y = daily.returns, color = "MGM")) + geom_line(data = FRC.CP, aes(x = index(FRC.CP), y = daily.returns, color = "FRC")) + geom_line(data = LUV.CP, aes(x = index(LUV.CP), y = daily.returns, color = "LUV")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("MGM" = "gold", "FRC" = "green", "LUV" = "red"))
chplt

chmrkplt <- ggplot() + geom_line(data = MGM.CP, aes(x = index(MGM.CP), y = daily.returns, color = "MGM")) + geom_line(data = FRC.CP, aes(x = index(FRC.CP), y = daily.returns, color = "FRC")) + geom_line(data = LUV.CP, aes(x = index(LUV.CP), y = daily.returns, color = "LUV")) + geom_line(data = bench.CP, aes(x = index(bench.CP), y = daily.returns, color = "Market")) + ggtitle("Closing Prices") + xlab("Date") + scale_color_manual(name = "Stock", values = c("MGM" = "gold", "FRC" = "green", "LUV" = "red", "Market" = "black"))
chmrkplt
```

\newpage


```{r echo=FALSE}
# try to get all on same table (company, symbol, return, risk, beta, p/e)
# Sclumberger Ltd. (SLB)
# Halliburton Company (HAL)
# CenterPoint Energy Inc.(CNP)
# Lowe's Companies, Inc. (LOW)
# Target Corporation (TGT)
# Walmart Inc. (WMT)
# MGM Resorts International (MGM)
# First Republic Bank (FRC)
# Southwest Airlines Co. (LUV)
financedata <- data.frame(Company = c( "Sclumberger Ltd.", "Halliburton Company", "CenterPoint Energy Inc.", "Lowe\'s Companies, Inc.", "Target Corporation", "Walmart Inc.", "MGM Resorts International", "First Republic Bank", "Southwest Airlines Co."), 
                          Symbol = c("SLB", "HAL", "CNP", "LOW", "TGT", "WMT", "MGM", "FRC", "LUV"), 
                          Return = round(c(SLB.mu.ann, HAL.mu.ann, CNP.mu.ann, LOW.mu.ann, TGT.mu.ann, WMT.mu.ann, MGM.mu.ann, FRC.mu.ann, LUV.mu.ann), 4)*100, 
                          Risk = round(c(SLB.sd.ann, HAL.sd.ann, CNP.sd.ann, LOW.sd.ann, TGT.sd.ann, WMT.sd.ann, MGM.sd.ann, FRC.sd.ann, LUV.sd.ann), 4)*100, 
                          Beta = round(c(SLB.beta, HAL.beta, CNP.beta, LOW.beta, TGT.beta, WMT.beta, MGM.beta, FRC.beta, LUV.beta), 2), 
                          PE = round(c(PESLB, PEHAL, PECNP, PELOW, PETGT, PEWMT, PEMGM, PEFRC, PELUV), 2))
financedata$Return <- paste0(as.matrix(financedata$Return), "%")
financedata$Risk <- paste0(as.matrix(financedata$Risk), "%")
#financedata
kable_styling(kbl(financedata, booktabs = T, format = "latex"), latex_options = "striped")
```

**Out of SLB, HAL, and CNP, SLB has the highest annualized expected return and a lower risk than HAL. CNP has the lowest return and the lowest risk. HAL is the most volatile out of the three stocks. SLB also has the highest PE Ratio compared to HAL and CNP.**  

**Between LOW, TGT, and WMT, LOW has the highest annualized expected return and the second lowest risk. TGT has a negative return but is the most volatile and has the second highest PE Ratio. WMT has the second lowest return, but has the lowest risk and highest PE Ratio out of the three stocks.**  

**When comparing last three stocks, MGM has the highest annualized expected return compared to FRC and LUV who both have negative returns; however, MGM does have the highest risk out of the three but is also the most volatile. LUV has the lowest return and beta but has the highest PE ratio.**  

**When comparing all nine stocks, SLB has the highest annualized expected return and the second highest annualized expected risk. LUV has the lowest return but the highest PE ratio. MGM is the most volatile and WMT is the least volatile.**




